Prediction maps of defoliation at trees

### 2019-05-24 analysis/report-defoliation.Rmd
update scripts

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super \
  /home/patrick/papers/2019-feature-selection/docs/figure/defoliation-maps.Rmd/* \
  -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/"
)
```

>>>>

```{r echo = FALSE}
system("rsync -rlptDvzog --chown=www-data:www-data --fake-super /home/patrick/papers/2019-feature-selection/docs/figure/report-defoliation.Rmd/* -e ssh patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/"
)
```
